Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
add scene duration, add cluter range
add new figs for ASSR, with correct p@k; rm JA comments in EMD description

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} \ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n$th bin to ``supply the demand'' of the $m$th bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=1-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

@@

In the experiments reported in this paper, the DCASE2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE2016 datasets  \cite{Mesaros2016_EUSIPCO} are considered. To build the DCASE2013 dataset, three different recordists visited a wide variety of locations in Greater London over
a period of several months and in each
scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

@@

Clustering is done using KMeans$++$ \cite{arthur2007k}, an augmented version of K-means with a robust initialization procedure.
\section{Results \label{sec:results}}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test3.eps}
\caption{ASSR: $p@k$ obtained for MFCCs and scattering with logarithmic compression.}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASSR: $p@k$ obtained for scattering with and without logarithmic compression.}
\label{fig:ASS_2}
\end{center}
\end{figure}

>>>>

\begin{equation*}
\sum\limits_{n,m}f_{nm} = \min\left( \sum\limits_{n} w_n^u ,\sum\limits_{m} w_m^v \right)
\end{equation*} 
%\ja{Can we provide some interpretation for the different terms and constraints here?}
where $\lbrace f_{nm} \rbrace$ is the flow between the cluster weights $w_n^u$ and $w_m^v$, that is, the amount transported from the $n$th bin to ``supply the demand'' of the $m$th bin. We denote by $D^{uv}$ the ground distance, a matrix containing the pairwise distances between the centroids sets $\mu^u$ and $\mu^v$. $D^{uv}$ is computed from the kernel $K$:
\begin{equation*}
D^{uv}=1-K^{(uv)}
\end{equation*}
with $K^{(uv)}$ being the slice of $K$ containing the pairwise similarities between the centroids sets $\mu^u$ and $\mu^v$ of the scenes $s_u$ and $s_v$ respectively. As suggested in \cite{pele2009fast}, we set the tradeoff parameter $\alpha$ to $1$.

@@

In the experiments reported in this paper, the DCASE2013 \cite{giannoulis2013database, 7100934} and the public part of the DCASE2016 datasets  \cite{Mesaros2016_EUSIPCO} are considered.

The DCASE2013  dataset consist of 2 parts, namely public and private, each made up of 100 30sec recordings of various acoustic scenes. The 100 recordings are equally divided into 10 acoustic scene classes. To build the DCASE2013 dataset, three different recordists visited a wide variety of locations in Greater London over a period of several months and in each scene recorded a few minutes of audio. No
systematic variations in the recordings covaried with scene
type: all recordings were made under moderate weather conditions, at varying times of day and week, and each recordist recorded each scene type. As a consequence, DCASE2013 dataset has interesting intra-class diversity while remaining manageable in terms of size, making it suitable for extensive evaluation of algorithmic design choices \cite{lagrange:hal-01082501}.

@@

Clustering is done using KMeans$++$ \cite{arthur2007k}, an augmented version of K-means with a robust initialization procedure. Three numbers of clusters are tested: 8, 16 and 32.

\section{Results \label{sec:results}}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test2.eps}
\caption{ASSR: $p@k$ obtained for MFCCs and scattering with logarithmic compression.}
\label{fig:ASS_1}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=8cm]{gfx/unsupervised_test1.eps}
\caption{ASSR: $p@k$ obtained for scattering with and without logarithmic compression.}
\label{fig:ASS_2}
\end{center}
\end{figure}
